\problemname{The Elk}
\noindent
You are in a forest. In this forest there is also a pair of elks 
- a cow (an adult female) and her calf (child). As most 
people know, it is dangerous to get between a cow and her calf, but it is not always clear how to avoid it.

We model our forest as consisting of $N$ locations, and $M$ direct connections 
between these locations. These connections can be travelled in either direction. 
The locations are numbered $0$ to $N-1$ and connections are numbered $0$ to $M-1$.

We define a path from the cow to the calf as a series of locations, $p_0, p_1, p_2, \ldots , p_k$ such that:
\begin{enumerate}
  \item $p_0$ is the location of the cow
  \item $p_k$ is the location of the calf.
  \item For each $i$ satisfying $0 \le i < k$, there is a direct connection between the locations $p_i$ and $p_{i+1}$
  \item None of the connections from point 3 are repeated within the path. Note that we \textbf{do allow locations} to be repeated within the path.
\end{enumerate}

Clearly, any location that is on any such path is a dangerous place to be, 
as the cow could consider you to be between her and the calf. Your task is to find all the safe locations - that is, the locations that are not on any such path.


\section*{Input}
The first line contains four integers, $N, M, A, B$. $N$ and $M$ are the 
number of locations and direct connections respectively, while $A$ and $B$ are the current locations of the cow and the calf respectively.

The following $M$ lines, numbered from $0$ to $M-1$, each describe one of the $M$ connections. 
The $i$th of these line contains two integers $U_i$ and $V_i$, indicating that $i$th connection is between locations $U_i$ and $V_i$.

\section*{Output}
The first line of output should contain a single integer $S$, the number of locations in the forest where it is safe to be.

The next $S$ lines of output should be a list of all the safe locations, 
one location per line, in increasing numerical order.

\section*{Constraints}
$2 \le N \le 5 \cdot 10^4$
\newline
$2 \le M \le 10^5$
\newline
$0 \le U_i, V_i < N$ for all $i$.
\newline
$0 \leq A,B \leq N-1$ 
\newline
$U_i \neq V_i$ for all $i$.
\newline
There will be at most one direct connection between any pair of locations.
\newline
There will always be at least one path from the cow to the calf.

\section*{Scoring}
Your solution will be tested on a set of test groups, each worth a number of points. 
Each test group contains a set of test cases. 
To get the points for a test group you need to solve all test cases in the test group.

\noindent
\begin{tabular}{| l | l | p{12cm} |}
  \hline
  \textbf{Group} & \textbf{Point value} & \textbf{Constraints} \\ \hline
  $1$    & $10$       & $N \le 10$, $M \le 45$  \\ \hline
  $2$    & $20$       & $M = N-1$ and the graph is connected. \\ \hline
  $3$    & $30$       & $N \le 200$, $M \le 500$ \\ \hline
  $4$    & $40$       & No additional constraints. \\ \hline
\end{tabular}

